KidsAIR home activity and characteristics cleaning

### 2020-03-12 demographics_summary.Rmd
Updates to summary stats/plots

---
title: "KidsAIR: household demographics summary"
author: "Ethan Walker"
date: "Started 27 Jan 2020, Updated 27 Jan 2020"
output: pdf_document
---

@@

>>>>

---
title: "KidsAIR: household demographics summary"
author: "Ethan Walker"
date: "Started 27 Jan 2020, Updated 12 March 2020"
output: pdf_document
---

@@

```{r}
# Filter for Winter 1; remove NAs

demographics_filtered <- demographics_clean %>% 
  filter(winter_id == 1) %>% 
  filter(!is.na(hispanic_child)) %>% 
  mutate(income = factor(income,
                         levels = c("Less than $20,000", "$20,000 to $29,999",
                                    "$30,000 to $39,999", "$40,000 to $49,999",
                                    "$50,000 to $74,999", "$75,000 to $99,999",
                                    "$100,000 or more")),
         education = factor(education,
                            levels = c("Less than high school",
                                       "High school diploma or GED",
                                       "Some college",
                                       "College degree")))
```

```{r}
# Demographics summary stats function

demographics_function <- function(data, var, title_label, y_label) {

  demographics_plot <- data %>% 
  filter(winter_id == 1) %>% 
  select(area, var) %>% 
  rename(plot_var = var) %>% 
  filter(!is.na(plot_var)) %>% 
  ggplot() +
    geom_bar(aes(plot_var, fill = area)) +
    theme_minimal() +
    theme(axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 40, vjust = 0.7, hjust = 0.7),
          axis.text.y = element_text(size = 16, colour = "black"),
          title = element_text(size = 18, colour = "black"),
          legend.text = element_text(size = 14, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(),
          panel.grid = element_blank()) +
    labs(title = title_label) +
    ylab(y_label) +
    scale_fill_manual(values = jv_palette)
  demographics_plot

}

demographics_function(demographics_filtered, "gender_parent", "Parent sex", "count")
demographics_function(demographics_filtered, "hispanic_parent", "Parent Hispanic ethnicity", "count")
demographics_function(demographics_filtered, "race_parent", "Parent race", "count")
demographics_function(demographics_filtered, "hispanic_child", "Child Hispanic ethnicity", "count")
demographics_function(demographics_filtered, "race_child", "Child race", "count")
demographics_function(demographics_filtered, "age_child_nov", "Child age Nov 1st", "count")
demographics_function(demographics_filtered, "income", "Household income", "count")
demographics_function(demographics_filtered, "education", "Parent education", "count")
demographics_function(demographics_filtered, "total_residents", "Total residents", "count")
demographics_function(demographics_filtered, "residents_under_five", "Residents under 5", "count")
```

### 2020-03-12 home_char_act_cleaning.Rmd
Updates to summary stats/plots

---
title: "KidsAIR home activity and characteristics cleaning"
author: "Ethan Walker"
date: "Started 13 Jan 2020, Updated 23 Jan 2020"
output: pdf_document
---

@@

home_char_clean <- kids_home_char %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id")) %>% 
  # cleaning based on checking odd values with paper logs
  mutate(residents_under5 = if_else(residents_under5 == 10, 1, residents_under5)) %>% 
  replace_with_na(replace = list(home_year_built = 0)) %>% 
  replace_with_na(replace = list(home_floors = 0)) %>% 
  replace_with_na(replace = list(home_windows = 0)) %>% 
  replace_with_na(replace = list(residents_total = 0)) %>% 
  replace_with_na(replace = list(residents_under5 = 0)) %>% 
  replace_with_na(replace = list(residents_under18 = 0)) %>% 
  replace_with_na(replace = list(home_sqft = 0)) %>% 
  mutate(home_year_built = if_else(home_year_built == 15, 2002, home_year_built),
         home_year_built = if_else(home_year_built == 874, 1980, home_year_built)) %>% 
  replace_with_na(replace = list(home_year_built = 1400)) %>% 
  mutate(home_sqft = if_else(home_sqft == 14 & home == "CH102", 360, home_sqft),
         home_sqft = if_else(home_sqft == 14 & home == "CH107", 1152, home_sqft)) %>% 
  replace_with_na(replace = list(home_sqft = 12)) %>% 
  replace_with_na(replace = list(home_sqft = 14)) %>% 
  replace_with_na(replace = list(home_sqft = 20)) %>% 
  replace_with_na(replace = list(home_sqft = 24)) %>% 
  replace_with_na(replace = list(home_sqft = 90)) %>% 
  mutate(home_furry = if_else(home_furry == 4 & home == "WMA368", 1, home_furry),
         home_furry = if_else(home_furry == 10 & home == "WMA345", 14, home_furry),
         home_furry = if_else(home == "WMA309", 3, home_furry),
         home_pets = if_else(home == "WMA309", 3, home_pets),
         home_pets = if_else(home == "WMA437", 3, home_pets),
         home_furry = if_else(home == "WMA437", 3, home_furry)) %>% 
  replace_with_na(replace = list(home_furry = 14)) %>% 
  ungroup() %>% 
  arrange(area, home, winter_id)

>>>>

---
title: "KidsAIR home activity and characteristics cleaning"
author: "Ethan Walker"
date: "Started 13 Jan 2020, Updated 4 March 2020"
output: pdf_document
---

@@

home_char_clean <- kids_home_char %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id")) %>% 
  # cleaning based on checking odd values with paper logs
  mutate(residents_under5 = if_else(residents_under5 == 10, 1, residents_under5),
         residents_under5 = if_else(home == "CH307" | home == "CH323", 1, residents_under5)) %>% 
  replace_with_na(replace = list(home_year_built = 0)) %>% 
  replace_with_na(replace = list(home_floors = 0)) %>% 
  replace_with_na(replace = list(home_windows = 0)) %>% 
  replace_with_na(replace = list(residents_total = 0)) %>% 
  replace_with_na(replace = list(residents_under5 = 0)) %>% 
  replace_with_na(replace = list(residents_under18 = 0)) %>% 
  replace_with_na(replace = list(home_sqft = 0)) %>% 
  mutate(home_year_built = if_else(home_year_built == 15, 2002, home_year_built),
         home_year_built = if_else(home_year_built == 874, 1980, home_year_built)) %>% 
  replace_with_na(replace = list(home_year_built = 1400)) %>% 
  mutate(home_sqft = if_else(home_sqft == 14 & home == "CH102", 360, home_sqft),
         home_sqft = if_else(home_sqft == 14 & home == "CH107", 1152, home_sqft)) %>% 
  replace_with_na(replace = list(home_sqft = 12)) %>% 
  replace_with_na(replace = list(home_sqft = 14)) %>% 
  replace_with_na(replace = list(home_sqft = 20)) %>% 
  replace_with_na(replace = list(home_sqft = 24)) %>% 
  replace_with_na(replace = list(home_sqft = 90)) %>% 
  mutate(home_furry = if_else(home_furry == 4 & home == "WMA368", 1, home_furry),
         home_furry = if_else(home_furry == 10 & home == "WMA345", 14, home_furry),
         home_furry = if_else(home == "WMA309", 3, home_furry),
         home_pets = if_else(home == "WMA309", 3, home_pets),
         home_pets = if_else(home == "WMA437", 3, home_pets),
         home_furry = if_else(home == "WMA437", 3, home_furry)) %>% 
  replace_with_na(replace = list(home_furry = 14)) %>% 
  ungroup() %>% 
  arrange(area, home, winter_id)
